Modeling Human Interactions in Collaborative Interactive Evolutionary Computation

### 2017-04-06 2017-GECCO-Modeling-User-Interactions-in-IEC/paper-short-body.tex
Paco's  suggestions

\section{Case Study: EvoDrawings Gamification}
\label{sec:evodraw}
As a case study, a C-IEC application was developed by extending the 
EvoSpace-Interactive (ES-I) platform \cite{garcia2013evospace}. 
The open source code is hosted in GitHub at
\url{https://github.com/mariosky/evo-drawings}. The rewarding 
mechanism as it is applied in EvoDrawings gives more importance 
to the preference of those users with higher reputation
as given by their score points and experience levels.  
Each time a user does on of these actions their score is incremented by one:
start a session, rate a phenotype, create a collection, save a phenotype of 
the wall to a collection, save a phenotypes from a friend's collection, and
explore collections of other friends. Each of these actions are stored in
the Neo4J graph. Two variables are used to determine the weight of a user's 
preference:

@@

Three versions of EvoDrawings were compared: Base (B): All users have the same weight,
Non Graph Gamification (G): Only experience is considered and Graph Gamification (GG): 
Both experience and participation are considered.

@@

\begin{acks}
This work has been supported in part by: de Ministerio espa\~{n}ol de Econom\'{\i}a y Competitividad under project TIN2014-56494-C4-3-P (UGR-EPHEMECH) and by Consejo Nacional de Ciencia y Tecnolog\'{\i}a under project 220590.

>>>>

\section{Case Study: EvoDrawings Gamification}
\label{sec:evodraw}
As a case study, a C-IEC application was developed by extending the 
EvoSpace-Interactive (ES-I) platform \cite{garcia2013evospace}. 
The open source code is hosted in GitHub at
\url{https://github.com/mariosky/evo-drawings}. The rewarding 
mechanism as it is applied in EvoDrawings gives more importance 
to the preference of those users with higher reputation
as given by their score points and experience levels.  
Each time a user does one of these actions their score is incremented by one:
start a session, rate a phenotype, create a collection, save a phenotype of 
the wall to a collection, save a phenotype from a friend's collection, and
explore collections of other friends. Each of these actions are stored in
the Neo4J graph. Two variables are used to determine the weight of a user's 
preference:

@@

Three versions of EvoDrawings were compared: Base (B): All users have the same weight;
Non Graph Gamification (G): Only experience is considered; and Graph Gamification (GG): 
Both experience and participation are considered.

@@

\begin{acks}
This work has been supported in part by: de Ministerio espa\~{n}ol de Econom\'{\i}a y Competitividad under project TIN2014-56494-C4-{1,2,3}-P (UGR-EPHEMECH), by Consejo Nacional de Ciencia y Tecnolog\'{\i}a under project 220590, and by Junta de Extremadura FEDER, project GR15068
